Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-04-05 papers/ms.tex
update ms

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present for the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets that directly confirms their planetary nature.
The most likely path for that would be through transit
observations with a high-resolution high-throughput spectrograph
\citep[see][]{bouma_kep1627_2022}.  In the interim, it is of some
interest whether any type of astrophysical false positive is likely to
explain the transit signals, or whether they can be argued to be
planetary on a statistical basis.  We adopt the Bayesian framework
implemented in \texttt{VESPA} for this purpose
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} take as given the binary star occurrence rate
from \citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each possible astrophysical model class, in which each
population member has a particular trapezoidal eclipse depth, total
duration, and ingress duration.  These summary statistics are then
compared against the actual photometric data to evaluate the 
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

@@

An interesting note on Kepler-1643 is that it formally fails the
default centroid shift test in both the \texttt{q1\_q17\_dr25\_koi}
and \texttt{q1\_q17\_dr25\_sup\_koi} releases, with the angular
distance between the target star position and the location of the
transiting source being reported as $0\farcs99$ (4.4-$\sigma$).  This
seems to be mostly due to two outlying quarters (Q2 and Q6) driving
the offset -- the centroid locations from the other Kepler quarters
are all consistent within $\lesssim 0\farcs5$.  Nonetheless, this is
an instructive exercise in how highly variable stars will complicate
centroid-based vetting tests.  The centroid shifts measured by these
tests are determined from the in- and out-of-transit flux-weighted
centroids, but for our stars there is no static baseline in either in-
or out-of-transit phase.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``CANDIDATE''
planet.  The Q1-Q17 DR25 False Positive Probability table however
lists its probability of being an astrophysical false positive as
``1.0''. However, given that none of the other columns in this table
are populated, this is most likely a database entry error ({\bf ask
Jessie}).  Performing the validation calculation using our new NIRC2
imaging constraints, we find ${\rm FPP} \approx 4\times10^{-3}$.
Though not as convincing as Kepler-1643, this formally clears the
usual threshold for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit itself is
$\approx 32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve.  Visually, one can also inspect
each individual transit window in the light curve itself.  This
exercise shows a weak notch in each case; over the 198 observed
transits, the resulting transit signal seems sensible.

Why was KOI-7368 not previously validated?  One reason could be the
increased stellar variability, or the lower S/N of the transit.
Another reason could be that it also formally fails the centroid shift
test, just like Kepler-1643.  In this case, the reported offset is
somewhat less significant ($0\farcs22$; 3.0-$\sigma$).  Again,
inspection of the data validation reports shows that this is caused by
a few outlying quarters: in this case Q4, Q5, Q8, and Q12.
The fact that the remaining quarters show a far more consistent
scatter suggests that these outliers are caused by local stellar
variability, rather than an astrophysical offset.
Our imaging also shows that there are no neighboring sources that
could cause the offset.

\paragraph{KOI-7913}
KOI-7913.01 is listed on the NASA Exoplanet Archive as a ``CANDIDATE''
planet.  The Q1-Q17 DR25 False Positive Probability table lists its
probability of being an astrophysical false positive as
$1.4\times10^{-4}$, with the most likely false positive scenario being
a blended eclipsing binary.  Repeating the calculation with our new
detrending and contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  While the transit has the lowest S/N of any of the
objects discusssed (${\rm S/N}=14$), its marginally lower FPP relative
to KOI-7368 can be understood through its relatively flat-bottomed
shape, combined with its long transit duration relative to plausible
eclipsing binary models.

The disposition of KOI-7913.01 seems to have been previously debated:
in \texttt{q1\_q17\_dr25\_koi} it was flagged as a ``FALSE POSITIVE'',
with the comment ``CENT\_KIC\_POS---HALO\_GHOST''.  This comment and
disposition seem to have been removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed it a
``CANDIDATE'', without any flag given.  As described by
\citet{thompson_planetary_2018}, the ``CENT\_KIC\_POS'' flag is an
indication that the measured source centroid is offset from its
expected location in the Kepler Input Catalog.  The final Data
Validation Reports (generated 2016 Jan 30) do not seem to show this,
and the statistical significance of any centroid offset seems to be
lower than for KOI-7368 and Kepler-1643 (which, as we have argued,
both show centroid offsets that seem to be explained by the stellar
variability).

What of the ``HALO\_GHOST'' flag?  This test measures the transit
strength for the pixels inside the aperture, and the ring of pixels
around that aperture (the ``halo'').  Generally one expects the
transit signal to be strongest in the central aperture.  Two types
of false positive scenarios can change this, triggering the flag: the first is
when optical ghosts from bright eclipsing binaries reflect off the
CCD, and contaminate the target star.  The second is when the PRF of
nearby stars directly overlaps with the PRF of the target star (see
\citealt{thompson_planetary_2018}, Section A.5.2).

@@

{\bf
TODO: words!  Describe Halo ghost statistic.  Why should I, or
shouldn't I, be worried?
}

%TODO : write a paragraph or two about previous VESPA work, and how we
% went further.

% Previous analyses have identified and characterized the smaller
% transit signal \citep{2012ApJS..199...24T,thompson_planetary_2018},
% validated its planetary nature \citep{morton_false_2016}, and even
% searched the system for transit timing variations
% \citep{holczer_transit_2016}.  Nonetheless, since the cluster
% membership provides us with more precise stellar parameters than those
% previously available, we opted to reanalyze the light curve.

>>>>

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present for the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep{kiman_calibration_2021}.  At $\approx$M0V, if
the secondary were in older than $\approx 500\,{\rm Myr}$, it would be
more common for its H$\alpha$ component to be observed in absorption
\citep[][Figure~4]{kiman_calibration_2021}.  H$\alpha$ emission in
late K-dwarfs is rarer still. Based on the data from K.~Rocio et al's
analysis\footnote{Available at
\url{https://zenodo.org/record/4659293#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature.  The
most likely path would be through transit observations using a
high-resolution spectrograph \citep[see][]{bouma_kep1627_2022}.  In
the interim, it is of interest whether the transit signals could be
astrophysical false positives, or whether they can be argued to be
planetary on a statistical basis.  We adopt the Bayesian framework
implemented in \texttt{VESPA} for this purpose
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} take as given the binary star occurrence rate
from \citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each possible astrophysical model class, in which each
population member has a particular trapezoidal eclipse depth, total
duration, and ingress duration.  These summary statistics are then
compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

@@

An interesting aside on Kepler-1643 is that it formally failed the
centroid shift test in the \texttt{q1\_q17\_dr25\_koi} data release,
with the angular distance between the target star position and the
location of the transiting source being reported as $0\farcs99$
(4.4-$\sigma$).  This seems to be mostly due to two outlying quarters
(Q2 and Q6) driving the offset -- the centroid locations from the
other Kepler quarters are all consistent within $\lesssim 0\farcs5$.
Nonetheless, this is an instructive exercise in how variable stars can
complicate centroid-based vetting tests.  The centroid shifts measured
by these tests are determined from the in- and out-of-transit
flux-weighted centroids, but for our stars there is no static baseline
in either in- or out-of-transit phase.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``CANDIDATE''
planet.  The Q1-Q17 DR25 False Positive Probability table however
lists its probability of being an astrophysical false positive as
``1.0''. However, given that none of the other columns in this table
are populated, this is likely a database entry error ({\bf ask
Jessie}).  Performing the validation calculation using our new NIRC2
imaging constraints, we find ${\rm FPP} \approx 4\times10^{-3}$.
While not as convincing as Kepler-1643, this formally clears the
usual threshold for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit itself is
$\approx 32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve.  Visually, one can also inspect
each individual transit window in the light curve itself.  This
exercise shows a weak notch in each case; over the 198 observed
transits, the resulting signal seems sensible.

Why was KOI-7368 not previously validated?  One reason could be the
high stellar variability.  Another reason could be that it also
formally fails the centroid shift test, similar to Kepler-1643.  In
the case of KOI-7368, the reported offset is marginally less
significant ($0\farcs22$; 3.0-$\sigma$).  Again, inspection of the
data validation reports shows that this is caused by a few outlying
quarters: in this case Q4, Q5, Q8, and Q12.  The fact that the
remaining quarters show a more consistent scatter suggests that these
outliers are again caused by stellar variability local to the
transits, rather than by an astrophysical offset.  Our imaging also
shows that there are no neighboring sources that could cause an
offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is listed on the NASA Exoplanet Archive as a ``CANDIDATE''
planet.  The Q1-Q17 DR25 False Positive Probability table lists its
probability of being an astrophysical false positive as
$1.4\times10^{-4}$, with the most likely false positive scenario being
a blended eclipsing binary.  Repeating the calculation with our new
detrending and contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  While the transit has the lowest S/N of any of the
objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).

The disposition of KOI-7913.01 has previously been debated:
in \texttt{q1\_q17\_dr25\_koi} the source was flagged as a ``FALSE POSITIVE'',
with the comment ``CENT\_KIC\_POS---HALO\_GHOST''.  This comment and
disposition seem to have been removed in the
\texttt{q1\_q17\_dr25\_sup\_koi} data release, which renamed it a
``CANDIDATE'', without any flag given.  As described by
\citet{thompson_planetary_2018}, the ``CENT\_KIC\_POS'' flag is an
indication that the measured source centroid is offset from its
expected location in the Kepler Input Catalog.  The final Data
Validation Reports, generated 2016 Jan 30, do not seem to show this.
Moreover, the statistical significance of any centroid offset seems to
be lower than for KOI-7368 and Kepler-1643 (which, as we have argued,
both show centroid offsets that seem to be explained by the stellar
variability).

What of the ``HALO\_GHOST'' flag?  This test measures the transit
strength for the pixels inside the aperture, and compares it to that
measured in the ring of pixels around said aperture (the ``halo'').
Generally one expects the transit signal to be strongest in the
central aperture, rather than the halo.  Two types of false positive
scenarios can change this and trigger the flag: the first is when
optical ghosts from bright eclipsing binaries reflect off the CCD, and
contaminate the target star.  The second is when the PRF of nearby
stars directly overlaps with the PRF of the target star (see
\citealt{thompson_planetary_2018}, Section A.5.2).

@@

As a test, we opted to re-extract the light curves from the target
pixel files for these particular cases.
{\bf Comparing the pixels on-target, and found}
%FIXME FIXME TODO TODO
{\bf We found...}
